Output Summary

### 2023-03-31 03-post-process/output-plots-children/02-mcmc-diags.Rmd
Remove MIN HOR quantities from MCMC diags
See #178

@@

This table displays summaries of MCMC diagnostics for all unobserved stochastic nodes in the model. Values in cells represent the percentage of parameters of a given type that fail a diagnostic check. E.g., 50% in the "Rhat > 1.05" column means that half of the parameters of that type had $\hat{R}$ values greater than 1.05. Cells with no color indicate no offense and darker reds indicate greater frequency of an offense.

>>>>

```{r discard-MIN-HOR}
# specify the nodes where Minam parameters aren't informed by data, and thus need no MCMC diagnostics
discard_params = c(
  "mu_phi_Mb_Ma[LH_type,origin,pop]",
  "^phi_Mb_Ma[year,LH_type,origin,pop]",
  "delta_O0_O1[pop]",
  "mu_psi_O1[origin,pop]",
  "^psi_O1[year,origin,pop]",
  "mu_psi_O2[origin,pop]",
  "^psi_O2[year,origin,pop]"
)

# replace the placeholder index names with the specific elements in question
no_mcmc_diags_Minam = lapply(discard_params, sub_index, pop = j_min) |>
  lapply(sub_index, LH_type = i_spring) |>
  lapply(sub_index, origin = o_hor) |>
  lapply(sub_index, year = ts_yrs) |>
  lapply(unique) |>
  unlist()

# remove these nodes from the posterior samples that will have MCMC diagnostics ran
diag_post = suppressMessages(post_remove(diag_post, params = no_mcmc_diags_Minam, ask = FALSE))
```

@@

This table displays summaries of MCMC diagnostics for all unobserved stochastic nodes in the model (excluding those that are not informed by data, such as HOR Minam maturation or HOR smolt survival; these parameters are sampled purely for organizational purposes in the model). Values in cells represent the percentage of parameters of a given type that fail a diagnostic check. E.g., 50% in the "Rhat > 1.05" column means that half of the parameters of that type had $\hat{R}$ values greater than 1.05. Cells with no color indicate no offense and darker reds indicate greater frequency of an offense.
